---
title: "Report Title"
subtitle: "Subtitle · Project or course name"
author: "Your Name"
date: today
date-format: "D MMMM YYYY"
lang: en  # or: nb — set logo to hvl-nb below to match

format:
  hvl-report-typst:
    number-sections: true

# Named logo resource from the HVL brand, placed by Quarto as a page background.
# English: hvl-en · Bokmål: hvl-nb. This is the *title page* logo; the raw Typst
# block below swaps it for the bare V mark from page 2 onward.
logo: hvl-en

execute:
  echo: true
  warning: false
  message: false
---

<!-- Page 1 is the title page. Quarto places the title block as a parent-scope
     float, so it lands on page 1 whatever follows; this break only keeps body
     text off that page. Everything below therefore starts on page 2. -->

{{< pagebreak >}}

<!-- The full logo named in `logo:` above repeats on every page, because that is
     what Quarto does with it — it becomes `page.background`. Re-setting the
     background here, after the break so page 1 is untouched, swaps it for the
     bare V mark from page 2 onward.

     `brand-logo-images` is a dictionary Quarto emits into the Typst source from
     brand.yml, with each path already resolved for wherever the brand extension
     actually sits. Going through it is what makes this work both in a clone
     (_extensions/hvl-brand/) and after `quarto add` (_extensions/<org>/hvl-brand/);
     a written-out path would work in exactly one of the two. The leading "/" makes
     it project-root-relative, and the geometry is copied from Quarto's own emitted
     call so the V lands exactly where the V inside the title-page logo does. -->

```{=typst}
#set page(background: align(left + top, box(
  inset: 0.75in,
  image(
    "/" + brand-logo-images.hvl-mark.path,
    width: 0.45in,
    alt: brand-logo-images.hvl-mark.alt,
  ),
)))
```

# Abstract {.unnumbered}

Summarise the work in a paragraph or two: what question was addressed, what was
done, and what came out of it. Write it so it stands on its own — a reader who
gets no further than this page should still know the result.

A heading is used here rather than the YAML `abstract:` key on purpose. That key
renders the abstract inside the title block on page 1, where it competes with the
title; as a section it gets a page of its own, ahead of the table of contents.

{{< pagebreak >}}

<!-- The table of contents, by hand. This is what article() would have emitted for
     `toc: true` — same depth and indent — but placed here, so the abstract can come
     first. Keep `toc: false` in the format (it is the extension default) or the
     document gets two of them. Translate the title with `lang: nb`:
     Innhaldsliste (nn) / Innholdsfortegnelse (nb). -->

```{=typst}
#block(below: 2em)[
  #outline(title: [Table of contents], depth: 3, indent: 1.5em)
]
```

{{< pagebreak >}}

# Foreword {.unnumbered}

Context that is not part of the work itself: who commissioned it, which project
or course it belongs to, who contributed, and any acknowledgements. Sign and date
it if that is the convention in your field.

If AI tools were used, say so here, along with what they were used for and who
takes responsibility for the content.

*Your Name, Place, 1 January 2026*

{{< pagebreak >}}

# Introduction

State the problem, why it matters, and what this report sets out to do. Sections
are numbered (`number-sections: true`); the abstract and foreword above are marked
`{.unnumbered}` so they stay outside the numbering.

Everything from here on is a working demonstration of the format — replace it
with your own sections.

# Working with the palette in R

This report inherits HVL colours, fonts, headings and link styling from
`_extensions/hvl-brand/brand.yml` — the same brand file that styles the RevealJS
deck in `presentation.qmd`. Body text is set in Lora, a close open-source match
to the profile font Lyon Text; headings use DM Sans in place of NB Akademie Std.
Typst downloads both from Google Fonts on first render and caches them, so neither
font needs to be installed locally.

Because the brand file is plain YAML, R can read the palette directly rather than
repeating hex codes. This keeps figures in step with the theme.

```{r}
#| label: palette
brand_path <- Sys.glob(c(
  "_extensions/hvl-brand/brand.yml", # rendering inside this repo
  "_extensions/*/hvl-brand/brand.yml" # installed via quarto add
))[1]

hvl <- yaml::read_yaml(brand_path)$color$palette
unlist(hvl[c("sea-green", "dark-blue-1", "dark-blue-2")])
```

# Figures and tables

Captions are set small and italic, figures and tables alike, so that a long
explanatory caption reads as a caption and not as another paragraph of body text.

## Figures

```{r}
#| label: fig-mpg
#| fig-cap: "Fuel efficiency against weight, coloured by cylinder count. Captions carry the explanation a reader needs to make sense of the figure without going back to the running text, which is why they are often several sentences long."
#| fig-height: 3.2
library(ggplot2)

ggplot(mtcars, aes(wt, mpg, colour = factor(cyl))) +
  geom_point(size = 2.5, alpha = 0.85) +
  scale_colour_manual(
    values = unname(unlist(hvl[c("sea-green", "dark-blue-1", "dark-blue-2")])),
    name = "Cylinders"
  ) +
  labs(x = "Weight (1 000 lbs)", y = "Miles per gallon") +
  theme_minimal(base_size = 11)
```

## Tables

| Campus | Students | Programmes |
|--------|---------:|-----------:|
| Bergen | 9 800 | 62 |
| Haugesund | 2 100 | 18 |
| Sogndal | 3 400 | 24 |
| Førde | 1 200 | 9 |

: Illustrative figures only. {#tbl-campus}

# Cross-references and links

@fig-mpg and @tbl-campus show the default Typst reference styling. Links such
as [hvl.no](https://www.hvl.no) take their colour from the brand's `primary`.

Inline code like `mean(mpg)` and blocks both use JetBrains Mono:

```r
summary_df <- mtcars |>
  dplyr::group_by(cyl) |>
  dplyr::summarise(mean_mpg = mean(mpg))
```

# Extending this format

`_extensions/hvl-report/_extension.yml` holds the whole format: a handful of
Typst show rules for captions and vertical rhythm, inline in the YAML, and
nothing else. There is no `.typ` template to maintain. Add document-specific
rules the way the page background above does it, in a ```` ```{=typst} ````
block, or move them into the extension if every HVL report should have them.

Brand values are readable from Typst as `brand-color.primary` and friends —
but only in the document body. Quarto inserts `include-in-header` *above* the
point where it defines `brand-color`, so an extension rule that names one fails
to compile with "unknown variable: brand-color"; write the colour out instead.
